Template \aastex Article with Examples: v6.3\footnote{Released on June, 10th, 2019}

### 2020-04-29 writeups/Su_disk_disp.tex
new bib file (need same name for arxiv)

%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%%        wider left and right margins. This uses the Daniel
%%        Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
    \documentclass[twocolumn,twocolappendix]{aastex63}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        graphicx,
        ae, aecompl,
        booktabs,
        caption,
        subcaption,
        xcolor,
    }
    \usepackage[T1]{fontenc}
    \captionsetup{compatibility=false}

@@

    \colorlet{Corr}{red}

    \newcommand{\vdag}{(v)^\dagger}
    \newcommand\aastex{AAS\TeX}
    \newcommand\latex{La\TeX}

@@

When $\theta_{\rm sd, i}\neq 0$, we find that the final obliquity $\theta_{\rm
f}$ spans a range of values for a given $\theta_{\rm sd, i}$, as can be
seen in Fig.~\ref{fig:nonad_3_ensemble}. The range can be described by
\begin{equation}
    \abs{\theta_{\rm 0f} - \theta_{\rm sd, i}}
        \lesssim \theta_{\rm f}
        \lesssim \theta_{\rm 0f} + \theta_{\rm sd, i}
    .\label{eq:nonad_q_f_dist}
\end{equation}
Eq.~\eqref{eq:nonad_q_f_dist} can be understood as follows (see
Fig.~\ref{fig:2nonadrot}). In the beginning ($\eta = \eta_{\rm i} \gg 1$), the
initial spin vector precesses around $\uv{l}_{\rm d}$ on a cone with opening
half-angle $\theta_{\rm sd, i}$ (more precisely, the cone is centered on CS2,
which coincides with $\uv{l}_{\rm d}$ as $\eta_{\rm i} \to \infty$). Note that
for $\eta \gg 1$, the adiabaticity condition is easily satisfied: using
$\theta_2 \simeq I + \eta^{-1}\sin I \cos I$ (see
Section~\ref{s:s:local_dynamics}), Eq.~\eqref{eq:w_lib} gives $\omega_{\rm lib}
\simeq \eta$ while Eq.~\eqref{eq:dq2dt} gives $\abs{\rdil{\theta_2}{\tau}}
\simeq \p{\epsilon / \eta} \sin I \cos I \ll \omega_{\rm lib}$. As $\eta$
decreases, the system will transition from being adiabatic to being
nonadiabatic, since $\epsilon \gtrsim \epsilon_{\rm c}$. The evolution of the
system can thus be decomposed into two phases: (i) when the evolution is
adiabatic, the spin vector will precess around the slowly-moving CS2; (ii) when
the evolution becomes nonadiabatic, the spin vector stops tracking the
quickly-evolving CS2. During the adiabatic evolution of phase (i), the angle
between CS2 and the spin vector is approximately unchanged due to conservation
of phase space area\footnote{ This approximation assumes sufficiently small
$\theta_{\rm sd, i}$ such that libration about CS2 remains approximately
circular throughout phase (i) (initially, when $\eta \to \infty$, all librations
are circular about $\uv{l}_{\rm d}$). This assumption breaks down when
$\theta_{\rm sd, i}$ is sufficiently large that librating orbits become
non-circular as $\eta$ decreases before the end of phase (i)
(Fig.~\ref{fig:eq_1contours} illustrates that the libration cycles farther from
CS2, corresponding to a larger $\theta_{\rm sd, i}$, are less circular for a
given $\eta$).
% Such deformations decrease the obliquity spanned by the cone (see
% Fig.~\ref{fig:eq_1contours} for decreasing $\eta$; note that level curves of $H$
% correspond to bases of cones), which causes the observed range of final
% obliquities in Fig.~\ref{fig:nonad_3_ensemble} to be smaller than predicted by
% Eq.~\eqref{eq:nonad_q_f_dist} when $\theta_{\rm sd, i} \gtrsim 45^\circ$.
This causes the deviation of the numerical results in
Fig.~\ref{fig:nonad_3_ensemble} from Eq.~\eqref{eq:nonad_q_f_dist} for
$\theta_{\rm sd, i} \gtrsim 45^\circ$. }.
Once the evolution enters phase (ii), the precession axis
quickly (on timescale $\ll 1 / \omega_{\rm lib}$) changes to $\uv{l}$ (as $\eta$
decreases to $\eta_{\rm f} \ll 1$). Precession about $\uv{l}$ does not change the
obliquity, so the range of obliquities at the end of phase (i) is frozen in as
the range of final obliquities.

@@

\bibliography{Su_sep_cross}
\bibliographystyle{aasjournal}

>>>>

    \documentclass[twocolumn,twocolappendix]{aastex63}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        graphicx,
        ae, aecompl,
        booktabs,
    }
    \usepackage[T1]{fontenc}

@@

    \newcommand\aastex{AAS\TeX}
    \newcommand\latex{La\TeX}

@@

When $\theta_{\rm sd, i}\neq 0$, we find that the final obliquity $\theta_{\rm
f}$ spans a range of values for a given $\theta_{\rm sd, i}$, as can be
seen in Fig.~\ref{fig:nonad_3_ensemble}. The range can be described by
\begin{equation}
    \abs{\theta_{\rm 0f} - \theta_{\rm sd, i}}
        \lesssim \theta_{\rm f}
        \lesssim \theta_{\rm 0f} + \theta_{\rm sd, i}
    .\label{eq:nonad_q_f_dist}
\end{equation}
Eq.~\eqref{eq:nonad_q_f_dist} can be understood as follows (see
Fig.~\ref{fig:2nonadrot}). In the beginning ($\eta = \eta_{\rm i} \gg 1$), the
initial spin vector precesses around $\uv{l}_{\rm d}$ on a cone with opening
half-angle $\theta_{\rm sd, i}$ (more precisely, the cone is centered on CS2,
which coincides with $\uv{l}_{\rm d}$ as $\eta_{\rm i} \to \infty$). Note that
for $\eta \gg 1$, the adiabaticity condition is easily satisfied: using
$\theta_2 \simeq I + \eta^{-1}\sin I \cos I$ (see
Section~\ref{s:local_dynamics}), Eq.~\eqref{eq:w_lib} gives $\omega_{\rm lib}
\simeq \eta$ while Eq.~\eqref{eq:dq2dt} gives $\abs{\rdil{\theta_2}{\tau}}
\simeq \p{\epsilon / \eta} \sin I \cos I \ll \omega_{\rm lib}$. As $\eta$
decreases, the system will transition from being adiabatic to being
nonadiabatic, since $\epsilon \gtrsim \epsilon_{\rm c}$. The evolution of the
system can thus be decomposed into two phases: (i) when the evolution is
adiabatic, the spin vector will precess around the slowly-moving CS2; (ii) when
the evolution becomes nonadiabatic, the spin vector stops tracking the
quickly-evolving CS2. During the adiabatic evolution of phase (i), the angle
between CS2 and the spin vector is approximately unchanged due to conservation
of phase space area\footnote{ This approximation assumes sufficiently small
$\theta_{\rm sd, i}$ such that libration about CS2 remains approximately
circular throughout phase (i) (initially, when $\eta \to \infty$, all librations
are circular about $\uv{l}_{\rm d}$). This assumption breaks down when
$\theta_{\rm sd, i}$ is sufficiently large that librating orbits become
non-circular as $\eta$ decreases before the end of phase (i)
(Fig.~\ref{fig:eq_1contours} illustrates that the libration cycles farther from
CS2, corresponding to a larger $\theta_{\rm sd, i}$, are less circular for a
given $\eta$).
% Such deformations decrease the obliquity spanned by the cone (see
% Fig.~\ref{fig:eq_1contours} for decreasing $\eta$; note that level curves of $H$
% correspond to bases of cones), which causes the observed range of final
% obliquities in Fig.~\ref{fig:nonad_3_ensemble} to be smaller than predicted by
% Eq.~\eqref{eq:nonad_q_f_dist} when $\theta_{\rm sd, i} \gtrsim 45^\circ$.
This causes the deviation of the numerical results in
Fig.~\ref{fig:nonad_3_ensemble} from Eq.~\eqref{eq:nonad_q_f_dist} for
$\theta_{\rm sd, i} \gtrsim 45^\circ$. }.
Once the evolution enters phase (ii), the precession axis
quickly (on timescale $\ll 1 / \omega_{\rm lib}$) changes to $\uv{l}$ (as $\eta$
decreases to $\eta_{\rm f} \ll 1$). Precession about $\uv{l}$ does not change the
obliquity, so the range of obliquities at the end of phase (i) is frozen in as
the range of final obliquities.

@@

\bibliography{Su_disk_disp}
\bibliographystyle{aasjournal}
